Descriptive stats and visuals

### 2020-09-21 manuscript/descriptive.Rmd
More work on manuscript
First working stan_jm models
Tweaks to derived data, updated data_description.md

```
```{r}
data$breathing_data %>% group_by(hospital_id, patient_id) %>%
  summarise(first = min(day, na.rm = TRUE)) %>%
  filter(first > 0)
```

@@

```{r}
outcome_data %>% filter(day > 30)
data$patient_data %>% filter(patient_id == "kOw52xii4l")
data_for_plot %>% filter(is.na(day))
```
```{r}
data$patient_data %>% filter(is.na(last_record))
```

>>>>

```
```{r}
data$patient_data %>% filter(hospital_id == "QKuFp") %>% select(first_day_invasive, last_day_invasive)
```

```{r}
data$breathing_data %>% group_by(hospital_id, patient_id) %>%
  summarise(first = min(day, na.rm = TRUE)) %>%
  filter(first > 0)
```

@@

```{r}
data$patient_data %>% filter(is.na(last_record))
```
